Efficient GPU implementation of multicomponent and multiphase Lattice Boltzmann models.

### 2010-05-25 paper.tex
Rewrap a number of paragraphs.

\item The binary-liquid models can be compared for the two-phase Poiseuille flow. The flow is driven by pressure gradient implemented as the force, $\frac{\mathrm{d}P}{\mathrm{d}x}$. The walls are implemented as a half-way bounce-back. It is known that BGK fails to reproduce the exact location of the wall. Instead of BGK we used the D2Q9 MRT model \cite{dhumieres-first,dhumieres}. While BGK operates with one parameter $\tau$, the MRT model operates with the number of eigenvalues, i.e. $s_{\rho},s_e,s_{\epsilon},s_{j_x},s_{q_x},s_{j_y},s_{q_y},s_{p_{xx}},s_{p_{xy}}$, giving better stability and proper the Navier-Stokes equation restoration by varying the free model eigenvalues \cite{dhumieres}.  For example for the half-way bounce-back walls representation for the Poiseuille flow the location of the wall is located exactly in the middle between nodes if the energy fluxes eigenvalues are defined as \cite{ginzburg-multireflection}:
\begin{equation}
\label{poiseuille:eigenvalues}
s_{q_{x,y}}=8\frac{2-\omega}{8-\omega},
\end{equation}
where $\omega$ states for the $s_{p_{xx}}$ and $s_{p_{xy}}$ related to the bulk and kinematic viscosities.

@@

We compare the models in terms of the accuracy for velocity profiles for different density and viscosity ratios and the calculation performance. The following summarizes our findings: {\color{red} Michal, please add here benchmarks}.   
\end{itemize}
\section{Conclusion}
%%%% Acknowledgments %%%%%%%%
\section*{Acknowledgments}
A.~Kuzmin wants to thank the Alberta Ingenuity Fund for their financial support.

>>>>

\item The binary-liquid models can be compared for the two-phase Poiseuille
	flow. The flow is driven by pressure gradient implemented as the force,
	$\frac{\mathrm{d}P}{\mathrm{d}x}$. The walls are implemented as a half-way
	bounce-back. It is known that BGK fails to reproduce the exact location of
	the wall. Instead of BGK we used the D2Q9 MRT model
	\cite{dhumieres-first,dhumieres}. While BGK operates with one parameter
	$\tau$, the MRT model operates with a number of eigenvalues, i.e.
	$s_{\rho},s_e,s_{\epsilon},s_{j_x},s_{q_x},s_{j_y},s_{q_y},s_{p_{xx}},s_{p_{xy}}$,
	giving better stability and proper the Navier-Stokes equation restoration
	by varying the free model eigenvalues \cite{dhumieres}.  For example for
	the half-way bounce-back walls representation for the Poiseuille flow the
	location of the wall is located exactly in the middle between nodes if the
	energy fluxes eigenvalues are defined as \cite{ginzburg-multireflection}:
\begin{equation}
\label{poiseuille:eigenvalues}
	s_{q_{x,y}}=8\frac{2-\omega}{8-\omega},
\end{equation}
where $\omega$ states for the $s_{p_{xx}}$ and $s_{p_{xy}}$ related to the bulk and kinematic viscosities.

@@

We compare the models in terms of the accuracy for velocity profiles for
different density and viscosity ratios and the calculation performance. The
following summarizes our findings: {\color{red} Michal, please add here
benchmarks}.

\end{itemize}
\section{Conclusion}
%%%% Acknowledgments %%%%%%%%
\section*{Acknowledgments}
A.~Kuzmin wants to thank the Alberta Ingenuity Fund for their financial support.
